---
title: "seqwraphelper"
format: gfm
---

`seqwraphelper` contains (a) functions that makes it easier to showcase [`seqwrap`](https://github.com/dhammarstrom/seqwrap). Using the function `geo_get()` we can download open datasets from the [Gene expression omnibus](https://www.ncbi.nlm.nih.gov/geo/). The function download, cleans and adds annotations to NCBI-generated gene count data. Two data frames are returned, one with meta-data and one with count data.

```{r}
#| eval: false

# install seqwraphelper from github
remotes::install_github("dhammarstrom/seqwraphelper")

```

The only dataset included in the main function is Shetty et al. (2024). To download the files:

```{r}

# Load package
library(seqwraphelper)

# Use geo_data to donload data from NCBI/GEO
dat <- geo_data()
```
The downloaded data sets are now available as two data frames.

```{r}

head(dat$countdata[,c(1, 2, 3)])

```

```{r}

head(dat$metadata)

```

## References

Shetty AC, Sivinski J, Cornell J, McCracken C et al. Peripheral blood transcriptomic profiling of molecular mechanisms commonly regulated by binge drinking and placebo effects. *Sci Rep* 2024 May 10;14(1):10733. PMID: 38730024
